% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{url}
\usepackage{hanging}
\usepackage{setspace}




% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {public policy, economics, statistics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9in},
  left=1in,
  top=1in
}

% Customize page headers
\pagestyle{myheadings}
\markright{Joshua D. Merfeld - CV}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\large}
\subsectionfont{\rmfamily\itshape\large}

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{0em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at center


\begin{center}
	{\Large \textbf{Joshua D. Merfeld}} \\
	merfeld [at] kdis.ac.kr \\
	
	\vspace{4mm}
	KDI School of Public Policy and Management \\
	263 Namsejong-ro, Sejong-si, South Korea, Office 343 \\
	+82-44-550-1023 \\
	\href{joshmerfeld.github.io/}{joshmerfeld.github.io/}
\end{center}


{\setstretch{0.5}

\vspace{0.5mm}

\section*{Academic Positions}
\vspace{-4mm}
\hrulefill
\begin{itemize}
  \item KDI School of Public Policy and Management
  	\subitem Assistant Professor (2020 - Present)
  \item Robert F. Wagner Graduate School of Public Service, New York University
  	\subitem Clinical Assistant Professor of Public Service (2018 - 2020)
  \item Department of Global Economics, Sungkyunkwan University
  	\subitem Lecturer (2017)
\end{itemize}


\section*{Research Affiliations}
\vspace{-4mm}
\hrulefill
\begin{itemize}
  \item Institute of Labor Economics (IZA)
  	\subitem Research Affiliate (2020 - Present)
  \item University of Washington Forum on Political Economy
  	\subitem Fellow (2020 - Present)
\end{itemize}


\vspace{0.5mm}

\section*{Publications}
\vspace{-4mm}
\hrulefill
\begin{itemize}
	\item ``Sectoral Wage Gaps and Gender in Rural India." IZA Discussion Paper No. 14391, available \href{https://www.iza.org/publications/dp/14391/sectoral-wage-gaps-and-gender-in-rural-india}{\underline{here}}, and most recent version, available \href{https://www.dropbox.com/s/df6xlk6wbe86r90/Merfeld_Wages.pdf?dl=0}{\underline{here}}. \textit{American Journal of Agricultural Economics}, forthcoming.
	\item ``The Importance of Specification Choices when Analyzing Sectoral Productivity Gaps'' with Peter Brummund (2022). \textit{Agricultural Economics,} \href{https://www.dropbox.com/s/s1tiqex7nnyt67o/Merfeld\%20and\%20Brummund\%20\%282021\%29.pdf?dl=0}{\textcolor{blue}{53(4): 605-616.}}
	\item ``Should Farmers Farm More? Comparing Marginal Products within Malawian Households'' with Peter Brummund (2021). \textit{Agricultural Economics,} \href{https://www.dropbox.com/s/xlrx6iwfqq2zlsl/Brummund\%20and\%20Merfeld\%20\%282021\%29.pdf?dl=0}{\textcolor{blue}{53(2): 289-306.}}
	\item ``Protecting Girls from Droughts with Social Safety Nets'' with Jagori Chatterjee (2021). \textit{World Development}, \href{https://www.dropbox.com/s/4s3219iybcqilhb/Chatterjee\%20and\%20Merfeld\%20\%282021\%29.pdf?dl=0}{\textcolor{blue}{Volume 147, 105624}}.
	\item ``Moving up or Just Surviving? Non-Farm Self-Employment in India'' (2020). \textit{American Journal of Agricultural Economics}, \href{https://www.dropbox.com/s/1qjwp0wj0g6m8iu/Merfeld\%20\%282020\%29.pdf?dl=0}{\textcolor{blue}{102(1), January 2020: 32-53}}.
	\item ``Spatially Heterogeneous Effects of a Public Works Program'' (2019). \textit{Journal of Development Economics}, \href{https://www.dropbox.com/s/l9ript8ubgpde3j/Merfeld\%20\%282019\%29.pdf?dl=0}{\textcolor{blue}{136, January 2019: 151-167}}.
	\item ``Relating Seasonal Hunger, Coping and Prevention Strategies, and Household Nutrition: A Panel Analysis of Malawian Farm Households'' with C. Leigh Anderson, Travis Reynolds, and Pierre Biscaye (2018). \textit{Journal of Development Studies}, \href{https://www.dropbox.com/s/bm3kps3zzfvm2c0/Anderson\%20et\%20al.\%20\%282018\%29.pdf?dl=0}{\textcolor{blue}{ 54(10), October 2018: 1737-1755}}.
\end{itemize}

\vspace{0.5mm}

\section*{Working Papers}
\vspace{-4mm}
\hrulefill
\begin{itemize}
	\item ``Combining Survey and Geospatial Data Can Significantly Improve Gender-Disaggregated Estimates of Labor Market Outcomes'' with David Newhouse, Michael Weber, and Partha Lahiri. World Bank Policy Research Working Paper 10077, available \href{https://documents.worldbank.org/en/publication/documents-reports/documentdetail/099321406092229138/idu016f95e0806fc6044ea0b843007d5dc0ef17e}{\underline{here}}. Revision requested, \textit{Journal of the Royal Statistical Society: Series A.}
	\item ``Labor Elasticities, Market Failures, and Misallocation: Evidence from Indian Agriculture.'' Most recent version (of IZA Discussion Paper No. 13682 and previously entitled ``Smallholders, Market Failures, and Agricultural Production: Evidence from India'') available \href{https://www.dropbox.com/s/g0pjo7v6z6tq2gg/Merfeld_Misallocation.pdf?dl=0}{\underline{here}}. Revision requested, \textit{Agricultural Economics.}
	\item ``Poverty at Higher Frequency" with Jonathan Morduch. Draft available \href{https://joshmerfeld.github.io/assets/papers/Merfeld_and_Morduch_(2022).pdf}{\underline{here}}. \textit{Under review.}
	\item ``Small Area Estimation of Monetary Poverty in Mexico using Satellite Imagery and Machine Learning'' with Anusha Pudugramam Ramakrishnan, Tom Swartz, and Partha Lahiri. World Bank Policy Research Working Paper 10175, available \href{https://documents.worldbank.org/en/publication/documents-reports/documentdetail/099430309142231728/idu0660868530404c0414e0bf180797b525682a5}{\underline{here}}. \textit{Under review.}
	\item ``Minimum wages and productivity shocks: Evidence from South Africa'' with Matthew Sharp. Draft available \href{https://joshmerfeld.github.io/assets/papers/MerfeldSharp2023.pdf}{\underline{here}}.
\end{itemize}

\vspace{0.5mm}


\section*{Works in Progress}
\vspace{-4mm}
\hrulefill
\begin{itemize}
	\item ``Validating approaches to poverty prediction: Small area estimation vs. machine learning'' with David Newhouse.
	\item ``Does the timing of the school year affect child labor decisions in developing countries?'' with Alex Eble.
	\item ``Gender and hiring in SMEs: Evidence from an RCT in Bangladesh" with Emily Beam and Asad Islam.
	\item ``Structural Transformation in a Changing Climate" with Rajeev Dehejia.
\end{itemize}

\vspace{0.5mm}


\section*{Other Work}
\vspace{-4mm}
\hrulefill
\begin{itemize}
	\item ``The Gambia poverty assessment'' with many others.
	\item ``Estimating Poverty in Borno State, Nigeria'' with Ryan Engstrom, David Newhouse, and M. Abul Kalam Azad.
	\item ``Structural Transformation in Sub-Saharan Africa'' with Gildas Deudibe, Justin Ndoutoumou, and David Newhouse. Note prepared for the Sub-Saharan Africa Team for Statistical Development, Poverty and Equity Global Practice, World Bank.
\end{itemize}

\vspace{0.5mm}


\section*{Awards}
\vspace{-4mm}
\hrulefill
\begin{itemize}
	\item 2022 Outstanding Reviewer Award, \textit{American Journal of Agricultural Economics.}
\end{itemize}



\vspace{0.5mm}

\section*{Service}
\vspace{-4mm}
\hrulefill
\begin{itemize}
	\item \textit{Referee service}: Review of Economics and Statistics, Journal of Public Economics, Journal of Development Economics, American Journal of Agricultural Economics, World Development, Food Policy, Journal of Official Statistics, Journal of Development Studies, Agricultural Economics, International Tax and Public Finance, Journal of Development Effectiveness, Social Indicators Research, Agribusiness
\end{itemize}

\vspace{0.5mm}


\section*{Funding}
\vspace{-4mm}
\hrulefill
\begin{itemize}
	\item ``The short-term effects of the Covid-19 lockdown on rural communities in India'' Co-I with Ashwini Desphpande, Kritika Saxena, and Lore Vandewalle (\textsterling19,952)
	\item KDI School research funding (KRW 35,160,000)
\end{itemize}


\vspace{0.5mm}



\section*{Presentations (Including Scheduled)}
\vspace{-4mm} 
\hrulefill
\begin{itemize}
	\item 2022: Tilburg; Penn State; IZA; IFAD; Agricultural Economics Society Annual Conference; IARIW; SMU (Singapore); NUS; IIM Calcutta; ANU Crawford
	\item 2021: Sungkyunkwan University; Korea University GSIS; Korea University Economics; Jobs and Development; Big4Small, SAE 2021; UN World Data Forum; ANU Crawford; Sogang University
	\item 2020: UC Dublin; KDI School, The Graduate Institute; Seoul National University
	\item 2019: NYU; Royal Economics Society; KDIS-3ie-ADB Conference on Impact Evaluation in Development Research; KER International Conference; NEUDC; Columbia; Econometric Society Winter Meetings
	\item 2018: AEA/ASSA; NYU
	\item 2017: Northwest Development Workshop; KEA/APEA; APPAM
	\item 2016: IATUR; Data for Policy; PNW Labor Day
	\item 2015: APPAM; STAARS
\end{itemize} 


\vspace{0.5mm}


\section*{Teaching Experience (Including Scheduled)}
\vspace{-4mm}
\hrulefill
\begin{itemize}
\item Development Economics (PhD)
\item Research Methods (PhD)
\item Analysis of Markets for Public Policy - Microeconomics (Masters)
\item Agriculture and Development (Masters)
\item Statistical Methods (Masters)
\item Using Large Datasets in Policy Research (Masters)
\item Designing Data Collection for Program Evaluation (Masters)
\item Capstone: Advanced Research Projects in Quantitative Analysis (Masters)
\item Quantitative Analysis for Public Policy (Undergrad)
\item Mathematics for Economics (Undergrad)
\end{itemize} 


\vspace{0.5mm}

\section*{Education}
\vspace{-4mm}
\hrulefill
\begin{itemize}
  \item \textbf{University of Washington}
	\subitem Ph.D. - Public Policy and Management (2018)
	\subitem MS - Public Policy and Management (2015)
	
\item \textbf{Georgia State University}
	\subitem MPP - Public Policy (2013)

\item \textbf{University of Georgia}
	\subitem B.A. - Spanish (2008)
\end{itemize}


\vspace{0.5mm}

\section*{Languages}
\vspace{-4mm}
\hrulefill
\begin{itemize}
	\item English (Native), Spanish (Fluent), Korean (Beginner)
\end{itemize}

\vspace{0.5mm}


\vfill

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
  \end{footnotesize}
\end{center}

\end{document}




